\begin{song}
{
title = {Zephyr Song},
interpret = {Red Hot Chilli Peppers}
}

\begin{verse}
^{Am}Can I get your hand to write on. ^{G}Just a piece of leg to bite on \\
^{Em}What a night to fly my kite on. ^{F}Do you want to flash your light on \\
^{Am}Take a look it’s on display \dots ^{G}for you. ^{Em}Comin' down, no not ^{F}today
\end{verse}

\begin{verse}
Did you meet your fortune teller. Get it off with no propeller \\
Do it up, it’s on with Stella. What a way to finally smell her \\
Pick it up, but not to strong … for you. Take a piece and pass it on
\end{verse}

\begin{chorus}
^{D}Fly away on my Zephyr. ^{G}I~feel it ^{A}more than ever \\
^{D}And in this perfect weather. ^{G}We’ll find ^{A}a~place together \\
^{Am}Fly ^{G}on \dots ^{Em}my ^{F}wind
\end{chorus}

\begin{verse}
Rebel and a liberator. Find a way to be a skater \\
Rev it up to levitate her. Super friendly aviator \\
Take a look it’s on display … for you. Comin’ down, no not today
\end{verse}

\begin{chorus}
Fly away on my Zephyr. I feel it more than ever \\
And in this perfect weather. We’ll find a place together \\
In the water where I center my emotion. All the world can pass me by \\
Fly away on my Zephyr. We’ll find a place together
\end{chorus}

\begin{solo}
\writechord{Am G Em F}
\end{solo}

\begin{interlude}
Whoa, whoa, whoa, whoa, whoa, whoa – do you \\
Yeah, yeah, yeah, yeah, yeah, yeah \\
Whoa, whoa, whoa, whoa, whoa, whoa – want to  \\
Yeah, yeah, yeah, yeah, yeah, yeah
\end{interlude}

\begin{chorus}
Fly away on my Zephyr. I feel it more than ever  \\
And in this perfect weather. We’ll find a place together \\
In the water where I center my emotion. All the world can pass me by \\
Fly away on my Zephyr. We’re gonna live forever
\end{chorus}




\end{song}